Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 overall.tex
correlation --> scatter plot.

\begin{figure*}%[htp]
    \includegraphics[clip,width=0.32\textwidth]{figures/titan_backfill_wnodes_distribution.pdf}
    \includegraphics[clip,width=0.32\textwidth]{figures/titan_backfill_walltime_distribution.pdf}
    \includegraphics[clip,width=0.32\textwidth]{figures/titan_backfill_avail.png}
    %figures/avail_time_vs_nodes_Oct_28_Nov_3_2015.pdf}
    \caption{Backfill availability: distribution of number of work nodes (left); distribution of walltime in minutes (center); and their correlation (right). 62175 measures: mean number of work nodes available 691; mean
    walltime available 126 minutes.}
\label{fig:backfill-distrib}
\end{figure*}

>>>>

\begin{figure*}%[htp]
    \includegraphics[clip,width=0.32\textwidth]{figures/titan_backfill_wnodes_distribution.pdf}
    \includegraphics[clip,width=0.32\textwidth]{figures/titan_backfill_walltime_distribution.pdf}
    \includegraphics[clip,width=0.32\textwidth]{figures/titan_backfill_avail.png}
    %figures/avail_time_vs_nodes_Oct_28_Nov_3_2015.pdf}
    \caption{Backfill availability: distribution of number of work nodes (left); distribution of walltime in minutes (center); and a scatter plot of the two variables (right). 62175 measures: mean number of work nodes available 691; mean
    walltime available 126 minutes.}
\label{fig:backfill-distrib}
\end{figure*}
